Parsing Postfix log files

### 2007-05-30 doc/logparser.tex
Fixed stupid bugs - I didn't fully reproduce the work I deleted earlier.

\subsection{execution time vs file size vs number lines}
\label{execution time vs file size vs number lines}
\includegraphics{plot-normal-filesize-numlines.ps}

\subsection{execution time vs file size vs number lines factor}
\label{execution time vs file size vs number lines factor}
\includegraphics{plot-normal-filesize-numlines-factor.ps}

\subsection{Regex: cached vs compiled every time}
\label{normal regex vs discard regex}
\includegraphics{plot-cached-discarded.ps}

>>>>

\subsection{Execution time vs file size vs number of lines.}
\label{execution time vs file size vs number lines}
\includegraphics{plot-normal-filesize-numlines.ps}

\subsection{Ratio of file size to execution time and number of lines to
execution time}
\label{execution time vs file size vs number lines factor}
\includegraphics{plot-normal-filesize-numlines-factor.ps}

\subsection{Regex: cached vs discarded}
\label{normal regex vs discard regex}
\includegraphics{plot-cached-discarded.ps}
